Methods with preconditioning with weight decay regularization

### 2023-03-30 paper/main.tex
Add files via upload

\section{Problem statement}

We consider the unconstrained optimization problem
\begin{equation*}
	\min_{w \in \mathbb{R}^d} f(w)
\end{equation*}
Problems of the form cover a plethora of applications, including empirical risk minimization,
deep learning, and supervised learning tasks such as regularized least squares or logistic regression.

@@

For solving these problems we always scaled adaptive gradients algorithms like ADAM, OASIS, ADAHessian. We investigate how the convergence rate will change when the regularization function is added to these algorithms.

% В исследуемом нами алгоритме сходимости мы будем исследовать алгоритмы двух следующих видов. В первом функция регуляризации выносится отдельном в пересчете весов модели, во втором функция домножается на обратный "гессиан".
In the convergence algorithm that we study, we will investigate algorithms of the following two kinds. In the first one, the regularization function is taken out separately in the recalculation of model weights, and in the second one, the function is dominated by the inverse "hessian".

>>>>

\section{Problem statement}
We want to investigate the convergence speed of the AdamW method and the newly proposed MyAdamW method in machine learning problems, and we also plan to prove the convergence of these methods and investigate the obtained solution.

We consider the unconstrained optimization problem
\begin{equation*}
	\min_{w \in \mathbb{R}^d} f(w)
\end{equation*}

@@

In the convergence algorithm that we study, we will investigate algorithms of the following two kinds. In the first one, the regularization function is taken out separately in the recalculation of model weights, and in the second one, the function is dominated by the inverse "hessian".
